RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-04-21 manuscripts/manuscript.Rmd
Update manuscript.Rmd

If the location parameter with which the `nexml_read()` method is
invoked is recognized as a URL, the method will automatically download
the document to the local working directory and read it from there. This
gives convenient and rapid access to phylogenetic data published in
NeXML format on the web, such as the content of the phylogenetic data
repository TreeBASE [@Piel_2002]. For example, the following plots a
tree in TreeBASE (using ape's plot function):

>>>>

If the location parameter with which the `nexml_read()` method is
invoked is recognized as a URL, the method will automatically download
the document to the local working directory and read it from there. This
gives convenient and rapid access to phylogenetic data published in
NeXML format on the web, such as the content of the phylogenetic data
repository TreeBASE [@Piel_2002; @Piel_2009]. For example, the following plots a
tree in TreeBASE (using ape's plot function):
